A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-09-24 main.tex
3.6.5 edits - in progress

\subsubsection{Tuning parameter selection}
Selection of the tuning parameter $\lambda$ plays an important role in all penalized regression methods, with many possible approaches.  Here, for each model, we selected the $\lam$ value such that 50 SNPs were selected (recall that 50 is also the true number of causal SNPs). This method for selecting $\lambda$ was chosen in an attempt to compare the performance of all methods fairly, and as a strategy to evaluate methods in terms of variable selection, as it allows for direct comparison of the first 50 variables each method lets into the model. \anna{make this sentence more getting at the point that we had concerns about using these common lambda selection methods... Although CV and information criterion-based methods are commonly used to select $\lambda$ values, in this context they have the potential to result in misleading comparisons across methods.} Alternative $\lambda$ selection methods were also considered. \anna{I know i have a citation for this somewhere FIND IT} Cross-validation may be inadvisable for LMMs, and in the presence of non-inedpendent samples as is the case here. While information criterion methods such as BIC present another option for selecting $\lambda$, they may be unstable in high dimensions. In addition, because Lasso, PC-Lasso, and LMM-Lasso use different likelihoods, an information-criterion-based approach would not lend itself to comparable results across methods.

1000 simulations were performed for each unique combination of parameters, datatype, subpopulation structure, and environmental effect structure.

>>>>

\subsubsection{Tuning parameter selection}
Selection of the tuning parameter $\lambda$ plays an important role in all penalized regression methods, with many possible approaches. Here, for each model, we selected the $\lam$ value such that 50 SNPs were selected (recall that 50 is also the true number of causal SNPs). This method for selecting $\lambda$ was chosen in an attempt to compare the performance of all methods fairly, and as a strategy to evaluate methods in terms of variable selection, as it allows for direct comparison of the first 50 variables each method lets into the model.

Although cross-validation and information criterion-based methods are commonly used to select $\lambda$ values, in this context they have the potential to result in misleading comparisons across methods. Cross-validation may be inadvisable for LMMs, and in the presence of non-inedpendent samples as is the case here \anna{I know i have a citation for this somewhere FIND IT}. While information criterion methods such as BIC present another option for selecting $\lambda$, they may be unstable in high dimensions. In addition, because Lasso, PC-Lasso, and LMM-Lasso use different likelihoods, an information-criterion-based approach would not lend itself to comparable results across methods.

1000 simulations were performed for each unique combination of parameters, datatype, subpopulation structure, and environmental effect structure. \anna{somewhere else to put this that makes more sense?}
